Visual proteomics using whole-lamella 2D template matching

### 2022-02-20 manuscript.tex
Don't deploy to gh-pages for now [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a8f7e15ca68cda59eec8dcd51b56efdb54e9344e.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/a8f7e15ca68cda59eec8dcd51b56efdb54e9344e/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/1873179503

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/27bee68862078e46176d358694eaaf9f82467d4e/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/27bee68862078e46176d358694eaaf9f82467d4e}{jojoelfe/deco\_lace\_template\_matching\_manuscript@27bee68}
on February 20, 2022.

>>>>

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/a8f7e15ca68cda59eec8dcd51b56efdb54e9344e/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/a8f7e15ca68cda59eec8dcd51b56efdb54e9344e}{jojoelfe/deco\_lace\_template\_matching\_manuscript@a8f7e15}
on February 20, 2022.
